# Course schedule {-}

## Monday 31st July {-}

*Introductions*

```{r, echo=FALSE}
times <- read.csv('data/sched.csv', sep=",",header=TRUE, stringsAsFactors = FALSE)
times$Date <- as.Date(times$Date, "%d/%m/%Y")
day <- dplyr::filter(times, Date == "2017-07-31")
#knitr::kable(
#  day[,2:4], booktabs = TRUE
#)
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

NB All activities will take place in the Training Suite, unless otherwise stated

## Tuesday 1st August {-}

*Resistance Proteins. Led by Jonathan Jones*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-01", Lead == "Jonathan Jones")
pander::pander(day[,2:4],justify = c('left', 'left', 'left'))

```

## Wednesday 2nd August {-}

*Resistance Proteins. Led by Jonathan Jones*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-02", Lead == "Jonathan Jones" )
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))
```

*Genomic Resources and Bioinformatics for Plant Microbe Interactions. Led by Dan MacLean*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-02", Lead != "Jonathan Jones")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```


## Thursday 3rd August {-}

*Effectors and Plant Immunity. Led by Sophien Kamoun*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-03", Lead == "Sophien Kamoun")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

## Friday 4th August {-}

*Effectors and Plant Immunity. Led by Sophien Kamoun*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-04", Lead == "Sophien Kamoun")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

*Surface Immunity. Led by Cyril Zipfel*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-04", Lead == "Cyril Zipfel")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))
```

## Saturday 5th August {-}

*Surface Immunity. Led by Cyril Zipfel*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-05", Lead == "Cyril Zipfel")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))
```

## Sunday 6th August {-}

*Excursion*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-06")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

## Monday 7th August {-}

*Cellular Defence. Led by Silke Robatzek*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-07", Lead == "Silke Robatzek")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

## Tuesday 8th August {-}

*Cellular Defence. Led by Silke Robatzek*

```{r, echo=FALSE}
day <- dplyr::filter(times, Date == "2017-08-08", Lead == "Silke Robatzek")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

*Wheat Genomics. Led by Ksenia Krasileva*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-08", Lead == "Ksenia Krasileva")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

## Wednesday 9th August {-}

*Proteomics. Led by Frank Menke*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-09")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

## Thursday 10th August {-}

*Translations and Tipping the Balance. Led by Matt Moscou and Peter Van Esse*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-10")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```

## Friday 11th August {-}

*Translations and Tipping the Balance. Led by Peter Van Esse and Matt Moscou*

```{r, echo=FALSE}

day <- dplyr::filter(times, Date == "2017-08-11")
pander::pander(day[,2:4], justify = c('left', 'left', 'left'))

```



